Curiosity-driven Exploration of Skill Hierarchies

### 2015-11-05 paper1/paper.tex
hierarchies
xp1 xp2

\section{Methods}

	\subsection{Algorithms}

		\paragraph{}
		Different module implementations (implemented):
		\begin{itemize}
			\item Motor Babbling,
			\item SAGG-Random.
		\end{itemize}

		\paragraph{}
		Different types of Sensorimotor models (implemented):
		\begin{itemize}
			\item NN or LWLR,
			\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}), or NSNN as NN with max gaussian\_kernel(distance) * gaussian\_kernel(time\_distance).
		\end{itemize}

		\paragraph{}
		Different possibilities to handle exploration in the hierarchy (implemented):
		\begin{itemize}
			\item MAB on all modules (greedy, softmax),
			\item MAB biaised on lower modules (see Sec. \ref{NSLWLR}),
			\item ZPDES (see Sec. \ref{zpdes}).
		\end{itemize}

		\paragraph{}
		Different types of Top-Down Drive:
		\begin{itemize}
			\item Just add noise to motor command of each module (pb: interferes with competence and progress estimation)  (implemented),
			\item Exploration budget around goals asked by higher models (explonential in $levels^{n+1}$ so even $n=1$ is not feasible in general but maybe in practice)  (implemented),
			\item Exploration budget only for the modules one layer below the babbling module (not implemented).
			\item Balance self-computed interest with Top-Down interest (implemented, based on the density of top-down goals).
		\end{itemize}

@@

	\subsection{Hierarchies}

		See Fig. \ref{Hierarchies} for exemples of hierarchies.

		\begin{figure*}[!t]
			\centerline{\subfloat[]{\input{include/H1.tikz}}
			\subfloat[]{\input{include/H2.tikz}}
			\subfloat[]{\input{include/H3.tikz}}
			\subfloat[]{\input{include/H4.tikz}}}
			\caption{Exemple of hierarchies.}
			\label{Hierarchies}					
		\end{figure*}
	%

	\subsection{Environment}

		\paragraph{}
		Different variables to test: motor and sensory dimensionalities, type of functions (linear, cosine, geometric arm, non-continuous interaction with objects), noise.

		\paragraph{Possible arm models}
		\begin{itemize}
			\item $n$ DOFs 2D geometric arm
		\end{itemize}

		\paragraph{Possible tool models}
		\begin{itemize}
			\item static piano
			\item stick 
		\end{itemize}

		\paragraph{Possible object models}
		\begin{itemize}
			\item static object with features depending on the piano
			\item dynamic object
		\end{itemize}

@@

	\subsection{Experiments}

			% Experiment 1
			\paragraph{Experiment 1: Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.}				
			\begin{itemize}
				\item Idea: to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig. \ref{Hierarchies}) to the control condition where a sensorimotor model is learned
						directly from the whole motor space $M$ to the whole sensori space $S$.

@@

			% Experiment 2
			\paragraph{Experiment 2: Which task should I explore now ?}
			\begin{itemize}
				\item Idea: to compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
						with the same hierarchy (a) of Fig. \ref{Hierarchies}.

@@

			% Experiment 3
			\paragraph{Experiment 3: How to choose between different means to explore a given space ?}
			\begin{itemize}
				\item Idea: to explain how we can choose between different means (e.g. different tools) using the one with the maximal competence, or maximal progress.
						We can use the hierarchy (b) of Fig. \ref{Hierarchies}, in order to have 2 different tools to move the object.

@@

			% Experiment 4
			\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
			\begin{itemize}
				\item Idea: to compare different possibilities of Top-Down Guidance, with hierarchy (c) of Fig. \ref{Hierarchies} in order to have TD guidance at different levels: 
						arm with one higher model, hand with 2 higher models, tool1 with one higher model, or tool2 with 2 higher models.

@@

			% Experiment 5
			\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}
			\begin{itemize}
				\item Idea: to apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
						We can use the hierarchy (d) of Fig. \ref{Hierarchies} in order to see an adaptation at 2 levels: the use of one hand to use one tool, the use of both tools to move the object even if only one is perturbated.

@@

\section{Results}

@@

\section{Discussion}

@@

\section{Conclusion}
The conclusion goes here.

@@

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

>>>>

\section{Environment}

	\begin{figure}[!t]
		\centering
		\includegraphics[width=8cm]{./include/tools.png}
		\caption{Play Environment}
		\label{env}
	\end{figure}

	See Fig. \ref{env} for the initial state of the environment.

@@

\section{Random Goal Babbling}

@@

\section{Hierarchically structured exploration}

	\begin{figure}[!t]
		\center
		\input{include/H1.tikz}
		\caption{H1}
		\label{H1}					
	\end{figure}

	% Experiment 1
	\subsection{Experiment 1: Methods}

		\begin{itemize}
			\item Idea: to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig. \ref{Hierarchies}) to the control condition where a sensorimotor model is learned
					directly from the whole motor space $M$ to the whole sensori space $S$.

@@

	\subsection{Experiment 1: Results}

		\begin{figure*}[!t]
			\centering
			\subfloat[Competences]{\includegraphics[width=6cm]{./include/H0-GB-log6-competences.png}}
			\subfloat[Interests]{\includegraphics[width=6cm]{./include/H0-GB-log6-interests.png}}
			\subfloat[Events]{\includegraphics[width=6cm]{./include/H0-GB-log6-events.png}}
			\caption{Competences, interests and events using H0 with Random Goal Babbling}
			\label{resH0GB}
		\end{figure*}

		\begin{figure*}[!t]
			\centering
			\subfloat[Competences]{\includegraphics[width=6cm]{./include/H1-GB-log5-competences.png}}
			\subfloat[Interests]{\includegraphics[width=6cm]{./include/H1-GB-log5-interests.png}}
			\subfloat[Events]{\includegraphics[width=6cm]{./include/H1-GB-log5-events.png}}
			\caption{Competences, interests and events using H1 with Random Goal Babbling}
			\label{resH1GB}
		\end{figure*}

		\begin{figure*}[!t]
			\centering
			\subfloat[Tool]{\includegraphics[width=6cm]{./include/xp1-n_tool_1.png}}
			\subfloat[Object]{\includegraphics[width=6cm]{./include/xp1-n_obj.png}}
			\subfloat[Box 1]{\includegraphics[width=6cm]{./include/xp1-n_box_1.png}}\\
			\subfloat[Box 2]{\includegraphics[width=6cm]{./include/xp1-n_box_2.png}}
			\subfloat[Box 3]{\includegraphics[width=6cm]{./include/xp1-n_box_3.png}}
			\caption{Number of touch of tool, object and boxes for each 100 iterations' bin.}
			\label{res_xp1_events}
		\end{figure*}

		See Fig. \ref{resH0GB}, \ref{resH1GB} and \ref{res_xp1_events}.

	\subsection{Experiment 1: Discussion}

\section{Choice of module to explore}

	% Experiment 2
	\subsection{Experiment 2: Methods}

		\begin{itemize}
			\item Idea: to compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
					with the same hierarchy (a) of Fig. \ref{Hierarchies}.

@@

	\subsection{Experiment 2: Results}

	\subsection{Experiment 2: Discussion}

\section{Choice of tool to use}

	\begin{figure}[!t]
		\center
		\input{include/H2.tikz}
		\caption{H2}
		\label{H2}					
	\end{figure}

	% Experiment 3
	\subsection{Experiment 3: Methods}

		\begin{itemize}
			\item Idea: to explain how we can choose between different means (e.g. different tools) using the one with the maximal competence, or maximal progress.
					We can use the hierarchy (b) of Fig. \ref{Hierarchies}, in order to have 2 different tools to move the object.

@@

	\subsection{Experiment 3: Results}

	\subsection{Experiment 3: Discussion}

\section{Top-Down Guidance}

	% Experiment 4
	\subsection{Experiment 4: Methods}	
	%\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}

		\begin{itemize}
			\item Idea: to compare different possibilities of Top-Down Guidance, with hierarchy (c) of Fig. \ref{Hierarchies} in order to have TD guidance at different levels: 
					arm with one higher model, hand with 2 higher models, tool1 with one higher model, or tool2 with 2 higher models.

@@

	\subsection{Experiment 4: Results}

	\subsection{Experiment 4: Discussion}

\section{Robustness to perturbations}

	% Experiment 5
	\subsection{Experiment 5: Methods}	
	%\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}

		\begin{itemize}
			\item Idea: to apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
					We can use the hierarchy (d) of Fig. \ref{Hierarchies} in order to see an adaptation at 2 levels: the use of one hand to use one tool, the use of both tools to move the object even if only one is perturbated.

@@

	\subsection{Experiment 5: Results}

@@

	\subsection{Experiment 5: Discussion}

	%\subsection{Algorithms}

		%\paragraph{}
		%Different module implementations (implemented):
		%\begin{itemize}
			%\item Motor Babbling,
			%\item SAGG-Random.
		%\end{itemize}

		%\paragraph{}
		%Different types of Sensorimotor models (implemented):
		%\begin{itemize}
			%\item NN or LWLR,
			%\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}), or NSNN as NN with max gaussian\_kernel(distance) * gaussian\_kernel(time\_distance).
		%\end{itemize}

		%\paragraph{}
		%Different possibilities to handle exploration in the hierarchy (implemented):
		%\begin{itemize}
			%\item MAB on all modules (greedy, softmax),
			%\item MAB biaised on lower modules (see Sec. \ref{NSLWLR}),
			%\item ZPDES (see Sec. \ref{zpdes}).
		%\end{itemize}

		%\paragraph{}
		%Different types of Top-Down Drive:
		%\begin{itemize}
			%\item Just add noise to motor command of each module (pb: interferes with competence and progress estimation)  (implemented),
			%\item Exploration budget around goals asked by higher models (explonential in $levels^{n+1}$ so even $n=1$ is not feasible in general but maybe in practice)  (implemented),
			%\item Exploration budget only for the modules one layer below the babbling module (not implemented).
			%\item Balance self-computed interest with Top-Down interest (implemented, based on the density of top-down goals).
		%\end{itemize}

\section{General Discussion}

@@

%\section{Conclusion}
%The conclusion goes here.

@@

% use section* for acknowledgement
%\section*{Acknowledgment}

%The authors would like to thank...
